\chapter{\abstractname}
 


The goal of this thesis is to develop a low-cost noninvasive vein viewing system on android smartphones that helps healthcare workers to identify the superficial veins, locate and examine them by providing an accurate AR image in a real-time manner. 
Venipuncture and starting an intravenous cannulation are frequently required skills in healthcare facilities for investigative or diagnostic purposes. Finding the right vein is a substantial prerequisite for such operations and could be time consuming, moreover, it is unfortunately not risk free as numerous associated complications have been described, including misplaced puncturing or even accidental arterial puncturing and cannulation, causing a life threat or unnecessary pain and stress to the patient in best cases.  
Dedicated devices for viewing and locating veins have been launched in the market, although they seem to give excellent results in terms of accuracy and performance, they include advanced and expensive hardware which makes them unaffordable for some countries or clinics.  

The proposed solution includes a low-cost hardware extension attached to a smartphone and an android application that receives and processes data sent from sensors placed on the hardware extension. On the smartphone’s screen, healthcare workers should be able to see a real-time video showing the superficial veins with good contrast and depending on that they can locate the veins and puncture them with much less probability of misplaced puncturing. 

We used NIR, Near Infrared, light source in wavelength of 940 nm and light sources as LEDs placed on an electrical circuit along with a digital video camera that only senses light waves in the infrared spectrum, which we obtained by replacing the light filters in a normal web camera. Because of NIR light-absorption properties of the oxygenated blood, which is carried by the veins, we were able to increase the peripheral veins’ contrast and, using image processing algorithms, visually isolate them on the received video in real-time.


